Hysteresis in human computation:\\ how one task affects another

### 2014-12-17 docs/publications/2014.09_SCIENCE/man.tex
fix a couple typos

It is difficult to measure the change in a probability distribution based on
samples alone (\#), so we reformulate the problem slightly. Consider that,  
no matter the ultimate purpose of a microtask study, a microtask response
is used in \textit{some kind} of subsequent decision or 
further processing.
We denote this dowstream decision by $\mathcal{D}$.  Since $\mathcal{D}$
takes a microtask response as input, biases in the microtask response will 
in general lead to biases in the output of $\mathcal{D}$.  
We can make use of this fact, 
by placing a machine learning algorithm (a classifier), in the role of 
$\mathcal{D}$.  This classifier takes as input a worker's responses to test 
tasks, from which it learns to infer the worker's treatment 
(i.e. the initial tasks she was given). 
Intuitively, the classifier's ability to infer the worker's treatment
depends on how strongly the exposure to prior tasks influences responses to 
subsequent ones.  Formally, the bias, $\theta$, is bounded 
by the accuracy of the classifier, $\eta$ (\#):
\begin{equation}
	\theta \geq 2\eta - 1.
	\label{l1}
\end{equation}
Thus, measuring the performance of the classifier allows us to establish a
lower bound on the extent of bias. This approach can be used to bound the 
bias induced by any purturbation, including both intertask effects and 
framing.  Bias ranges from 0 (meaning there are no intertask effects), to 1 
(or 100\%) (meaning that changing initial tasks leads to a completely 
different set of responses to test tasks).

@@

We conducted variants of these experiments using different images, to see 
whether this trend was robust.  In the experiment 
\textit{intertask-food-culture},
workers were either assigned to a \textit{food} or \textit{culture} treatment.
As before, the initial tasks for the \textit{food} treatment contained images 
depicting food (\#) (see Fig.~\ref{fig:task}D). 
In the \textit{culture} treatment, 
the initial tasks contained images depicting cultural scenes 
(of dance, sport, or music) (see Fig.~\ref{fig:task}E).  The test tasks, which were identical for both
treatments, included images depicting meals of identifiable cultural 
origin 
(see Fig.~\ref{fig:task}F).  Results for this experiment again showed a 
strong bias (about 50\%; see Fig.~\ref{fig:theta}A) between the labels 
provided by workers from the two 
treatmens during test tasks.  Again, we compared intertask effects to framing,
by performing an experiment (\textit{frame-food-culture}) using 
the same test tasks as in \textit{intertask-food-culture}, in which we exposed
workers to a statement framing the purpose of the tasks as the recognition 
of either food or cultures.  
For this framing experiment, we did not observe a statistically significant 
difference between the labels attributed by the \textit{food} and 
\textit{culture} treatments during test tasks (see Fig.~\ref{fig:theta}).

@@

	\paragraph{Variance in food specificity.}
	The variance in the specificity measurements was calculated using a 
	bootstrapping proceedure.  For two given treatments $A$ and $B$, 
	119 workers were sampled from each with replacement, giving the bootstrap
	samples $A'$ and $B'$, and the relative specificity between these 
	was measured as described in \textsection S6.
	This was repeated 1000 times.  The 2.5 and 97.5 percentiles were used
	to create the 95\% confidence intervals.

>>>>

It is difficult to measure the change in a probability distribution based on
samples alone (\#), so we reformulate the problem slightly. Consider that,  
no matter the ultimate purpose of a microtask study, a microtask response
is used in \textit{some kind} of subsequent decision or 
further processing.
We denote this downstream decision by $\mathcal{D}$.  Since $\mathcal{D}$
takes a microtask response as input, biases in the microtask response will 
in general lead to biases in the output of $\mathcal{D}$.  
We can make use of this fact, 
by placing a machine learning algorithm (a classifier), in the role of 
$\mathcal{D}$.  This classifier takes as input a worker's responses to test 
tasks, from which it learns to infer the worker's treatment 
(i.e. the initial tasks she was given). 
Intuitively, the classifier's ability to infer the worker's treatment
depends on how strongly the exposure to prior tasks influences responses to 
subsequent ones.  Formally, the bias, $\theta$, is bounded 
by the accuracy of the classifier, $\eta$ (\#):
\begin{equation}
	\theta \geq 2\eta - 1.
	\label{l1}
\end{equation}
Thus, measuring the performance of the classifier allows us to establish a
lower bound on the extent of bias. This approach can be used to bound the 
bias induced by any perturbation, including both intertask effects and 
framing.  Bias ranges from 0 (meaning there are no intertask effects), to 1 
(or 100\%) (meaning that changing initial tasks leads to a completely 
different set of responses to test tasks).

@@

We conducted variants of these experiments using different images, to see 
whether this trend was robust.  In the experiment 
\textit{intertask-food-culture},
workers were either assigned to a \textit{food} or \textit{culture} treatment.
As before, the initial tasks for the \textit{food} treatment contained images 
depicting food (\#) (see Fig.~\ref{fig:task}D). 
In the \textit{culture} treatment, 
the initial tasks contained images depicting cultural scenes 
(of dance, sport, or music) (see Fig.~\ref{fig:task}E).  The test tasks, which were identical for both
treatments, included images depicting meals of identifiable cultural 
origin 
(see Fig.~\ref{fig:task}F).  Results for this experiment again showed a 
strong bias (about 50\%; see Fig.~\ref{fig:theta}A) between the labels 
provided by workers from the two 
treatments during test tasks.  Again, we compared intertask effects to 
framing,
by performing an experiment (\textit{frame-food-culture}) using 
the same test tasks as in \textit{intertask-food-culture}, in which we exposed
workers to a statement framing the purpose of the tasks as the recognition 
of either food or cultures.  
For this framing experiment, we did not observe a statistically significant 
difference between the labels attributed by the \textit{food} and 
\textit{culture} treatments during test tasks (see Fig.~\ref{fig:theta}).

@@

	\paragraph{Variance in food specificity.}
	The variance in the specificity measurements was calculated using a 
	bootstrapping procedure.  For two given treatments $A$ and $B$, 
	119 workers were sampled from each with replacement, giving the bootstrap
	samples $A'$ and $B'$, and the relative specificity between these 
	was measured as described in \textsection S6.
	This was repeated 1000 times.  The 2.5 and 97.5 percentiles were used
	to create the 95\% confidence intervals.
